A Cross-Domain Benchmark for Active Learning

### 2024-06-06 doc/al_benchmark_paper.tex
Remove acknowledgement, it breaks page limit
anonymous github link

In summary, \emph{CDALBench} is an experimental framework which includes an
efficient oracle approximation, multiple application domains, enough repetitions to
draw valid conclusions and two synthetic tasks to highlight shortcomings of AL methods. 
By being the first benchmark to providing these points in one code-base, 
we believe that \emph{CDALBench} is a major step forward of assessing the overall state of AL research, independent of
specific application domains. \emph{CDALBench} is publicly available under \url{https://github.com/wernerth94/A-Cross-Domain-Benchmark-for-Active-Learning/}. \\ [1mm]
Our contributions include the following:
%
\begin{enumerate}
\item\label{cont:repetitions} We show that the small number of repetitions that previous works have employed is not
sufficient for meaningful conclusions. Sometimes even making it impossible to assess if a performance is above or below random.
\item\label{cont:oracle} We propose an efficient and performant oracle which is constructed iteratively in a greedy fashion,
overcoming major computational hurdles.
% one of the major obstacles for sufficient repetitions of AL experiments. 
% [Thorben] Das können wir so nicht sagen, glaube ich. Niemand verlangt von uns, dass wir das Oracle auch 50 mal wiederholen
\item\label{cont:domains} We propose \emph{CDALBench}, the first general benchmark providing tasks
in the domains of image, text and tabular learning. It further contains
synthetic and pre-encoded data to allow for a sophisticated evaluation of AL
methods. Our experiments show, that there is no clear SOTA method
for AL across different domains.
\item\label{cont:synthdata} We propose \emph{Honeypot} and \emph{Diverging Sin}, two synthetic datasets
designed to hinder AL by naive decision-boundary- or
clustering-based approaches respectively. Thus, they provide an important tool to identify 
shortcomings of existing AL methods.
\end{enumerate}

@@

\newpage
\paragraph{Acknowledgement}
anonymous
%TODO
%Funded by the Lower Saxony Ministry of Science and Culture under grant number ZN3492 within the Lower Saxony “Vorab“ of the Volkswagen Foundation and supported by the Center for Digital Innovations (ZDIN).

>>>>

In summary, \emph{CDALBench} is an experimental framework which includes an
efficient oracle approximation, multiple application domains, enough repetitions to
draw valid conclusions and two synthetic tasks to highlight shortcomings of AL methods. 
By being the first benchmark to providing these points in one code-base, 
we believe that \emph{CDALBench} is a major step forward of assessing the overall state of AL research, independent of
specific application domains. \emph{CDALBench} is publicly available under %\url{https://github.com/wernerth94/A-Cross-Domain-Benchmark-for-Active-Learning/}. 
\url{https://anonymous.4open.science/r/A-Cross-Domain-Benchmark-for-Active-Learning-CCB1/README.md}
\\ [1mm]
Our contributions include the following:
%
\begin{enumerate}
\item\label{cont:repetitions} We show that the small number of repetitions that previous works have employed is not
sufficient for meaningful conclusions. Sometimes even making it impossible to assess if a performance is above or below random.
\item\label{cont:oracle} We propose an efficient and performant oracle which is constructed iteratively in a greedy fashion,
overcoming major computational hurdles.
% one of the major obstacles for sufficient repetitions of AL experiments. 
% [Thorben] Das können wir so nicht sagen, glaube ich. Niemand verlangt von uns, dass wir das Oracle auch 50 mal wiederholen
\item\label{cont:domains} We propose \emph{CDALBench}, the first general benchmark providing tasks
in the domains of image, text and tabular learning. It further contains
synthetic and pre-encoded data to allow for a sophisticated evaluation of AL
methods. Our experiments show, that there is no clear SOTA method
for AL across different domains.
\item\label{cont:synthdata} We propose \emph{Honeypot} and \emph{Diverging Sin}, two synthetic datasets
designed to hinder AL by naive decision-boundary- or
clustering-based approaches respectively. Thus, they provide an important tool to identify 
shortcomings of existing AL methods.
\end{enumerate}

@@

% \newpage
% \paragraph{Acknowledgement}
% anonymous
%TODO
%Funded by the Lower Saxony Ministry of Science and Culture under grant number ZN3492 within the Lower Saxony “Vorab“ of the Volkswagen Foundation and supported by the Center for Digital Innovations (ZDIN).
